### 2021-04-15 papers/SYRCoSE/intro.tex
Isabelle -> Isabelle/HOL
Isabelle is a framework, not a proof assistant per se

The programming languages theory and formal semantics research communities 
are moving to increase the usage of \emph{proof assistants} 
like Coq, Agda, Isabelle, Arend, and others,
to complement theoretical studies with their mechanisation,
as this process increases the reliability and reproducibility 
of scientific results.
Yet, to the best of our knowledge, there is little work on 
mechanisation of the theory of event structures.
The present report aims to close the gap.

>>>>

The programming languages theory and formal semantics research communities 
are moving to increase the usage of \emph{proof assistants} 
like Coq, Agda, Isabelle/HOL, Arend, and others,
to complement theoretical studies with their mechanisation,
as this process increases the reliability and reproducibility 
of scientific results.
Yet, to the best of our knowledge, there is little work on 
mechanisation of the theory of event structures.
The present report aims to close the gap.
